Hybrid Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-13 manuscript/main.tex
compactness condition as lemma

@@

between the response and the scalar predictor:

@@

@@

 The following proposition presents several important properties of $\mathcal{U}$.
	\begin{proposition} \label{Proposition: property of U}
	 Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that

@@

			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in [0,1]} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,

@@

		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in [0,1]$ with $|t_k - t_k^* | < \delta_k$, we have that
			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,

@@

	\end{proposition}
	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.

>>>>

	\begin{equation}\label{def:cross_covariance_yx}

@@

and between the response and the scalar predictor:

@@

		Then $\mathcal{U}$

@@

To guarantee the existence of a complete orthonormal system of eigenfunctions for $\mathcal{U}$ in $\mathcal{H}$, we  first demonstrate that $\mathcal{U}$ is compact.
To this end, we begin by defining the notion of uniform continuity for the cross-covariance function defined in \eqref{def:cross_covariance_yx}:
\begin{definition}[Uniform Continuity]\label{def:uniform_continuity}
	For each $k \in \{1, \ldots, K\}$, the cross-covariance function $\sigma_{YX, k} \in \mathcal{F}$ is uniformly continuous if for any $\epsilon > 0$, there exists a $\delta_k > 0$ such that for all $t_1, t_2 \in [0,1]$ satisfying $|t_1 - t_2 | < \delta_k$, we have
		| \sigma_{YX, k} (t_1) - \sigma_{YX, k} (t_2) | < \epsilon.
\end{definition}
Using this definition, the following lemma presents a condition for $\mathcal{U}$ to be a compact operator.
	\begin{lemma}[Compactness condition] \label{Proposition: property of U}
If there exist finite constants $Q_1$ and $Q_2$ such that

@@

			\max \limits_{k=1, \ldots, K} \sup \limits_{t \in [0,1]} \sigma_{YX, k}^{2}(t) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,

@@

		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous,

@@

The proof of Lemma \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
